{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-30 bmvc_review.tex
Paper Updated - PF, CFs Order, Some More Updates

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed} Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while perserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflow_figure}.

\item \textbf{Re-Detection} A target loss is inevitable in object
  tracking. To cope with this, we developed a new target, re-detection
  that reliably detects when to lose the target and effectively
  re-detect the lost target. {\it How we can show how good our
    re-detection method is?}

\begin{comment}
\item We build a highly efficient ($\geq300$ fps) scale adaptive
  multiple kernelized correlation filter based tracker that
  outperforms the original KCF implementation with fixed scale
  framework both in terms of accuracy and performance. The studies
  following the KCF improved the fixed scale framework by running
  detection on a number of candidate ROIs to figure out the new scale
  of the object after estimating the translation of the object. This
  approach adds additional complexity to the original KCF
  implementation and drags down the run-time performance from $300$
  fps to less than $100$ fps.

@@

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%----------------------------------------------------------------------

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
\label{Workflow_figure}
\end{figure*}

@@

After Heriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high}, many variation of KCF were
investigated. In particular, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is particularly similar to that of
\cite{ma2015long} in that more than one KCF is used to address the
challenges of single target tracking. But ours is different from that
of \cite{ma2015long} in that we do not use those three KCFs together
at every frame, but alternatively at every three frame. The way our
algorithm is alternating multiple KCFs in different goals intuitively
makes sense in that the appearance of consecutive images does not
change much. Although it varies based on the scene, learning a
correlation filter a frame would not be much different from the one
learned using the image few or $k$ frames later. By alternating three
KCFs in turn, our algorithm runs as fast as or faster than the
original KCF. From our experiments, we empirically found that five is
the optimal for $k$ in terms of precision and success rates. We'll
detail this at the experimental section later.

@@

The order of deploying these three KCFs is {\it Burak: Answer this}

The \textit{target+large background} translation filter, $R_{t}^{L}$,
is designed to run in right next frame after the scale filter,
$R_s$. We deploy these two filters in this way because we want to
minimize any drifts, which are likely to happen running only $R_{s}$.

{\it Burak: Rewrite the following two sentences.}

Considering a large ROI for $R_{t}^{L}$ can degrade its performance
due to information loss resulting from ROI resizing.

On the other hand, only HoG features are used in $R_{t}^{S}$ as it
focuses on a smaller ROI, giving us more discriminative HoG
features.

The reason why our {\it E}nKCF comes with two KCF for translation {\it
  Burak: Answer this.}

In our framework, $R_{t}^{S}$ addresses the absence of scale
adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$
focuses on addressing the absence of translation estimation module in
$R_{S}$.

$R_{t}^{S}$, on the other hand, focuses on the shape features
of the target that is not fully exploited in $R_{t}^{L}$ and
$R_{t}^{S}$. For this reason, we employ \textit{HoG} features in
$R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in
$R_{t}^{L}$. Fig.~\ref{Workflow_figure} displays the proposed tracking
framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of
the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.

\begin{algorithm}
	\caption{The EnKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
		         \State Skip it for $R_{t}^{L}$ (Condition 1),
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
				\State // Update Translation
				\State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
				\If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
				\State Update $R_{s}$ (Condition 1);
				\EndIf							 
				\If{$PSR(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
				\State Update $R_{t}^{L}$ (Condition 2);
				\EndIf	
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

@@

\subsection{Particle Filter} \label{sc:PF}
The proposed MKCF algorithm can cause undesired drift and noise in
tracking due to independent application of the correlation filters. To
mitigate the drift effect and reduce the noise, a Bayes Filter
representing the evolution of target's motion can be added into the
MKCF tracking framework. In this study, we consider a variant of a
Bayes Filter, \textit{Particle Filter}. The Particle Filter is a
Sequential Monte Carlo method that can approximate posterior
probability density functions (pdf) of a target motion. The
approximation becomes optimal with the infinite number of particles,
however, its run-time complexity grows exponentially with the number
of elements in the state space matrix, $X_{t}$. As the focus of this
study is to design a high speed tracker, we keep the number of state
space elements low and implement computationally cheap \textit{Weight
  Function} and \textit{Importance-Resampling} modules. We represent
the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$
where $x$ and $y$ are the centroid of the target and $V$ represents
the velocity components. We transit the particles with the well-known
first order Constant Velocity model. The centroid components are
applied Gaussian Noise whereas the velocity components are assigned
uniform noise representative of most of the objects. The observation
likelihood is modeled based on the confidence map of
$R_{t}^{L}$,$R_{t}^{S}$, and $R_{s}$. It can also be modeled based on
the euclidean distance between particle's centroid to the peak of the
confidence maps, however, we believe that the former approach could
result in further drifts in the case of multi-modal distributions. The
weights for the particles are computed with the bilinear interpolation
method.
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \dfrac{y_{R}(x_{t}-1,y_{t}-1)+y_{R}(x_{t}+1,y_{t}+1){y_{R}(x_{t}+1,y_{t}-1)+y_{R}(x_{t}-1,y_{t}+1)}}{4}
\end{equation}
where $w_{p}$ denotes the weight of the particle. The importance
re-sampling module is triggered when the number of effective particles
is smaller than a pre-defined threshold [Cite - Effective Number
  Samples Metric] to avoid variance getting too small. Re-sampling is
implemented with highly efficient low-variance ratio method
[cite]. Finally, the expected mean of the approximated posterior pdf
is computed as
\begin{equation}
	\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}
\end{equation}

The particles are assigned equal weight ($\dfrac{1}{P}$) after the
importance re-sampling step. It should be emphasized that we skip
importance re-sampling step in the scale filter operation as the scale
filter contains \textit{target-only} area. In this case, the particles
outside of the scale filter ROI do not have weight correspondence in
the confidence map. Also, it is more likely to get noisy translation
estimation from the scale filter.

@@

\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the
committee of the correlation filters are important as the each
correlation filter addresses the weakness of another one. For
instance, $R_{t}^{L}$'s main task is to recover from the previous
frame where only $R_{s}$ and particle filter's prior distribution are
used to estimate scale and translation. We set the learning rates
($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$
and $0.010$. The desired response and hanning window for each KCF is
shown in fig.~\ref{fig:Filters}. Finally, the Gaussian kernel
parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. In our particle filter
implementation, we employ $1000$ particles and use the
\textit{efficient number of samples} metric shown below to determine
whether we need to perform importance re-sampling or not to keep
reasonable variance.
\begin{equation}
  \hat{N}_{eff} = \dfrac{1}{\sum_{i=1}^{P}(w_{p})^{2}}, 
\end{equation}
 where $w$ represents the particles' weights and re-sampling is performed only if $\hat{N}_{eff}$ is smaller than three.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset. UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions. Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}
\label{fig:UAV123_DATASET}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_OTB100.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
\label{fig:OTB100_DATASET}
\end{figure}
%\begin{figure}
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
%        \end{subfigure}%
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
%        \end{subfigure}%
%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset. UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions. Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
%\end{figure}
%
%\begin{figure}
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
%        \end{subfigure}%
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
%        \end{subfigure}%
%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures. }\label{fig:OTB100_DATASET}
%\end{figure}

\textbf{Overall Performance without Re-detection on UAV123 Dataset.}
We compare the proposed tracker to other state-of-the-art high speed
trackers using the \textit{Precision} and \textit{Success\:Rate}
metrics. Precision is computed by thresholding the average euclidean
distance between the ground truth and tracking output over the frames
of one sequence. In precision, we rank the trackers based on the
precision numbers at 20 pixels. The success rate metric evaluates the
overlap between the ground truth and tracking output. The
intersection-to-union ratio of two regions over the frames of one
sequence. Finally, we count the number of frames with overlap larger
than the success rate threshold and divide it by the number of
frames. We compare our tracker to some other high-speed ($\geq$300
fps) state-of-the-art trackers including KCF\cite{henriques2015high},
CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset. The E$n$KCF tracker outperforms the other methods in
high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision
accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on
the same dataset although it is $10$-$20$ times faster than these
trackers. On the other hand, the E$n$KCF does a decent job on
approximating the scale of the target in highly efficient manner. This
is proved by the fact that it ranks third best tracker in terms of
\textit{area under curve} (AUC) value for the success rate plot. It
outperforms the high speed trackers by about $20\%$-$25\%$ in AUC
metric. Interestingly, it performs even better than most of the low
speed trackers. For instance, it outperforms Struct and DSST by $5\%$
and $10\%$ while running at more than $30$ and $10$ times larger
operation rate.

\textbf{Overall Performance without Re-detection on OTB100 Dataset.}
In addition to UAV123 dataset, we test the E$n$KCF tracker on the
OTB100 dataset to evaluate how good it generalizes to a traditional
object tracking dataset. Again, it performs slightly better than the
high speed trackers in precision. Interestingly, it outperforms the
another correlation filter based tracker, DSST while running only
$5\%$ behind of another low-speed scale adaptive SAMF tracker. As in
UAV123 dataset, the E$n$KCF performs exceptionally in handling the
scale changes. It is ranked as the fifth best tracker while being the
second highest speed tracker behind MOSSE. It performs only around
$2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers
prove that E$n$KCF is not only a good candidate for tracking on a
UAV-based mobile platform but also mobile platforms on smart phones.

>>>>

The contributions of this study are as follows.
\begin{itemize}
\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
  efficiently address the scale variance and the dynamic maneuver of a
  target while perserving run-time performance as high as possible. To
  minimize any potential performance gap from transiting one KCF to
  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
  be visualized in fig.~\ref{Workflow_figure_EnKCF}. The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
  datasets.

\item \textbf{Slight Modification of the proposed EnKCF for Handling Large Motion} Our second algorithm, 
{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose. The original {\it E}nKCF is slighlty modified to track fast motions and handle large ego-motion. We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on the low frame rate UAV platform. Particle Filter can be deployed in case the camera motion is known. The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.

\begin{comment}\item \textbf{Re-Detection} A target loss is inevitable in object
  tracking. To cope with this, we developed a new target, re-detection
  that reliably detects when to lose the target and effectively
  re-detect the lost target. {\it How we can show how good our
    re-detection method is?}

\item We build a highly efficient ($\geq300$ fps) scale adaptive
  multiple kernelized correlation filter based tracker that
  outperforms the original KCF implementation with fixed scale
  framework both in terms of accuracy and performance. The studies
  following the KCF improved the fixed scale framework by running
  detection on a number of candidate ROIs to figure out the new scale
  of the object after estimating the translation of the object. This
  approach adds additional complexity to the original KCF
  implementation and drags down the run-time performance from $300$
  fps to less than $100$ fps.

@@

%---------------------------------------------------------------------- 
\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
%---------------------------------------------------------------------- 
\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
\label{Workflow_figure_EnKCF}
\end{figure*}

\begin{figure*}[!t]
\centering
\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
\label{Workflow_figure_EnKCF2}
\end{figure*}

@@

After Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high}, many variation of KCF were
investigated. In particular, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is particularly similar to that of
\cite{ma2015long} in that more than one KCF is used to address the
challenges of single target tracking. But ours is different from that
of \cite{ma2015long} in that we do not use those three KCFs together
at every frame, but alternatively at every three frame. The way our
algorithm is alternating multiple KCFs in different goals intuitively
makes sense in that the appearance of consecutive images does not
change much. Although it varies based on the scene, learning a
correlation filter a frame would not be much different from the one
learned using the image few or $k$ frames later. By alternating three
KCFs in turn, our algorithm runs as fast as or faster than the
original KCF. From our experiments, we empirically found that five is
the optimal for $k$ in terms of precision and success rates. We'll
detail this at the experimental section later.

@@

The order of deploying these three KCFs is critical as they need to run with full coherency to perfom robust tracking. The \textit{target+large background} translation filter, $R_{t}^{L}$, is designed to run in right next frame after the scale filter, $R_s$, which is applied at every $n=5$ frames. We deploy these two filters in this way because we want to minimize any drifts, which are likely to happen running only $R_{s}$. Finally, $R_{t}^{S}$ is applied in two consecutive frames before $R_{S}$ and right after two consecutive frames implementation of $R_{t}^{L}$. This way, we can integrate more discriminative shape features that can not be fully learned by $R_{t}^{L}$ as it contains contribution of large background in the learned model. On the other hand, $R_{t}^{L}$ uses shape and color information together to do a better job in recovering from any drifts due to application of $R_{s}$ in previous frame. In this framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$ and $R_{t}^{S}$ addresses the weakness of $R_{t}^{L}$ that it can not learn very useful shape features alone. Fig.~\ref{Workflow_figure_EnKCF} displays the proposed high-speed tracking framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of
the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.

\begin{algorithm}
	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
		         \State Skip it for $R_{t}^{L}$ (Condition 1),
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
				\State // Update Translation
				\State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
				\If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
				\State Update $R_{s}$ (Condition 1);
				\EndIf							 
				\If{$PSR(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
				\State Update $R_{t}^{L}$ (Condition 2);
				\EndIf	
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

@@

\subsection{Particle Filter} \label{sc:PF}
The proposed {\it E}nKCF algorithm can cause undesired drift and noise in
tracking due to independent and less frequent application of the correlation filters. To
mitigate the drift effect further and reduce the noise, a Bayes Filter
representing the evolution of target's motion can be added into our
{\it E}nKCF tracking framework. To achieve this, we consider a variant of a
Bayes Filter, \textit{Particle Filter}. The Particle Filter is a
Sequential Monte Carlo method that uses a number of sample points to represent
the posterior probability density functions (pdf) of the target motion. 
The approximation becomes optimal with the infinite number of particles,
however, its run-time complexity grows exponentially with the number
of elements in the state space matrix, $X_{t}$. As the focus of this
study is to design a high speed tracker, we keep the number of state
space elements low and implement computationally efficient \textit{Weight
  Function} and \textit{Importance-Resampling} modules. We represent
the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$
where $x$ and $y$ are the centroid of the target and $V$ represents
the velocity components. We transit the particles with the first order Constant Velocity model. The centroid components are applied Gaussian Noise whereas the velocity components are assigned
uniform noise representative of most of the objects in our tests. The observation
likelihood is formulated based on the confidence map of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. 
The weights for the particles are computed as
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the size of the window in consideration. We can also use the spatial distance of particles to the peak of the confidence map, however, we believe that this approach could result in further drifts in the case of multi-modal distributions.

The importance re-sampling module is triggered when the number of effective particles
is smaller than a pre-defined threshold to avoid variance getting too small \cite{thrun2005probabilistic}. Re-sampling is implemented with efficient low-variance ratio method \cite{thrun2005probabilistic}. Finally, the expected mean of the approximated posterior pdf is computed as
\begin{equation}
	\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}.
\end{equation}
The particles are assigned equal weight after the importance re-sampling step in approximating the posterior pdf. It should be emphasized that we skip importance re-sampling step in the scale filter 
operation as the scale filter contains \textit{target-only} area. In this case, the particles
outside of the scale filter ROI do not have correspondence in the confidence map. Additionally, it is more likely to get noisy confidence map from $R_{s}$. Finally, at every iteration we check the variance in the velocity components of the particles to re-assign velocities from uniform initial distribution to keep variance high enough.

@@

\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the
committee of the correlation filters are important as the each
correlation filter addresses the weakness of another one. For
instance, $R_{t}^{L}$'s main task is to recover from the previous
frame where only $R_{s}$ and particle filter's prior distribution are
used to estimate scale and translation. We set the learning rates
($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$
and $0.010$. The desired response and hanning window for each KCF is
shown in fig.~\ref{fig:Filters}. Finally, the Gaussian kernel
parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. In our particle filter
implementation, we employ $1000$ particles and use the
\textit{efficient number of samples} metric shown below to determine
whether we need to perform importance re-sampling or not to keep
reasonable variance.

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_UAV123.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 dataset. UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions. Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}
\label{fig:UAV123_DATASET}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_OTB100.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_OTB100.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
\label{fig:OTB100_DATASET}
\end{figure}

%\begin{figure}
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
%        \end{subfigure}%
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
%        \end{subfigure}%
%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset. UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions. Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
%\end{figure}
%
%\begin{figure}
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
%        \end{subfigure}%
%        \begin{subfigure}{0.5\textwidth}
%                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
%        \end{subfigure}%
%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures. }\label{fig:OTB100_DATASET}
%\end{figure}

\textbf{Overall Performance on UAV123 Dataset.}
We compare the proposed tracker to other state-of-the-art high speed
trackers using the \textit{Precision} and \textit{Success\:Rate}
metrics. Precision is computed by thresholding the average euclidean
distance between the ground truth and tracking output over the frames
of one sequence. In precision, we rank the trackers based on the
precision numbers at 20 pixels. The success rate metric evaluates the
overlap between the ground truth and tracking output. The
intersection-to-union ratio of two regions over the frames of one
sequence. Finally, we count the number of frames with overlap larger
than the success rate threshold and divide it by the number of
frames. We compare our tracker to some other high-speed ($\geq$300
fps) state-of-the-art trackers including KCF\cite{henriques2015high},
CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset. The {\it E}nKCF tracker outperforms the other methods in
high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision
accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on
the same dataset although it is $10$-$20$ times faster than these
trackers. On the other hand, the {\it E}nKCF does a decent job on
approximating the scale of the target in highly efficient manner. This
is proved by the fact that it ranks third best tracker in terms of
\textit{area under curve} (AUC) value for the success rate plot. It
outperforms the high speed trackers by about $20\%$-$25\%$ in AUC
metric. Interestingly, it performs even better than most of the low
speed trackers. For instance, it outperforms Struct and DSST by $5\%$
and $10\%$ while running at more than $30$ and $10$ times larger
operation rate.

\textbf{Overall Performance on UAV123$\_$10fps Dataset.}

\textbf{Overall Performance on OTB100 Dataset.}
In addition to UAV123 dataset, we test the {\it E}nKCF tracker on the
OTB100 dataset to evaluate how good it generalizes to a traditional
object tracking dataset. Again, it performs slightly better than the
high speed trackers in precision. Interestingly, it outperforms the
another correlation filter based tracker, DSST while running only
$5\%$ behind of another low-speed scale adaptive SAMF tracker. As in
UAV123 dataset, the {\it E}nKCF performs exceptionally in handling the
scale changes. It is ranked as the fifth best tracker while being the
second highest speed tracker behind MOSSE. It performs only around
$2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers
prove that {\it E}nKCF is not only a good candidate for tracking on a
UAV-based mobile platform but also mobile platforms on smart phones.
